---
title: "CHL5208 Code"
author: "Peiqing Yu"
date: "2026/7/13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(survival)
```

## 1. Simulation Scenario definition

```{r}
get_scenario_params <- function(scenario) {
  
  params <- list(
    beta_trt = 0,
    utility_fun = function(t) 0,
    base_fun = function(t) 0.65 + 0.15 * (1 - exp(-t / 8))
  )
  
  if (scenario == "A") {
    # Null: no survival or utility difference
    params$beta_trt <- 0
    params$utility_fun <- function(t) 0
  }
  
  if (scenario == "B") {
    # Survival benefit only
    # HR = exp(-0.80) = 0.45
    params$beta_trt <- -0.80
    params$utility_fun <- function(t) 0
  }
  
  if (scenario == "C") {
    # Utility benefit only
    params$beta_trt <- 0
    params$utility_fun <- function(t) 0.18
  }
  
  if (scenario == "D") {
    # Early harm, late benefit
    params$beta_trt <- -0.40
    params$utility_fun <- function(t) {
      ifelse(t <= 12, -0.08,
             ifelse(t <= 30, 0.04, 0.24))
    }
  }
  
  if (scenario == "E") {
    # Longer survival, worse QoL
    params$beta_trt <- -0.75
    params$utility_fun <- function(t) -0.12
  }
  
  if (scenario == "F") {
    # Better QoL, shorter survival
    params$beta_trt <- 0.60
    params$utility_fun <- function(t) 0.18
  }
  
  if (scenario == "G") {
    # Benefit in both survival and utility
    # This is your strongest demonstration of QALY/HUS
    params$beta_trt <- -0.65
    params$utility_fun <- function(t) 0.16
  }
  
  return(params)
}

```

## 2. Data generation
- 2.1 Covariates
- 2.2 Treatment assignment
- 2.3 Survival outcome
- 2.4 Utility trajectories
- 2.5 Missingness
```{r}
simulate_data <- function(
  n0 = 150,
  n1 = 150,
  tt = 60,
  scenario = "A",
  observational = TRUE,
  
  # treatment assignment model
  # severity is the main source of observational confounding
  alpha = c(alpha0 = 0, age = 0.00, sex = 0.00, sev = 0.65),
  
  # survival model
  beta = c(beta0 = -4.0, age = 0.025, sex = 0.025, sev = 0.6),
  shape = 1.2,
  
  # utility model
  theta = c(age = -0.01, sex = -0.01, sev = -0.1),
  sigma_subject = 0.08,
  sigma_noise = 0.04,
  
  # missingness
  p_miss = 0.05,
  
  seed = NULL
) {
  
  if (!is.null(seed)) set.seed(seed)
  
  params <- get_scenario_params(scenario)
  
  ##################################################
  # 1. Generate large covariate pool
  ##################################################
  
  n_pool <- 10000
  
  age <- runif(n_pool, 35, 80)
  sex <- rbinom(n_pool, 1, 0.5)
  sev <- rnorm(n_pool, 0, 1)
  
  # Center and scale covariates
  age_c <- (age - 57.5) / 10
  sex_c <- sex - 0.5
  
  ##################################################
  # 2. Treatment assignment
  ##################################################
  
  if (observational) {
    linpred_trt <- alpha["alpha0"] +
      alpha["age"] * age_c +
      alpha["sex"] * sex_c + 
      alpha["sev"] * sev
    
    prob_trt <- plogis(linpred_trt)
    trt_all <- rbinom(n_pool, 1, prob_trt)
  } else {
    trt_all <- rbinom(n_pool, 1, 0.5)
  }
  
  id1_pool <- which(trt_all == 1)
  id0_pool <- which(trt_all == 0)
  
  if (length(id1_pool) < n1 | length(id0_pool) < n0) {
    stop("Not enough subjects in one treatment group. Adjust alpha or n_pool.")
  }
  
  id1 <- sample(id1_pool, n1)
  id0 <- sample(id0_pool, n0)
  
  age1 <- age[id1]
  age0 <- age[id0]
  
  sex1 <- sex[id1]
  sex0 <- sex[id0]
  
  sev1 <- sev[id1]
  sev0 <- sev[id0]
  
  ##################################################
  # 3. Survival model
  ##################################################
  
  lin0 <- beta["beta0"] +
    beta["age"] * (age0 - 57.5)/10 +
    beta["sex"] * (sex0 -0.5) +
    beta["sev"] * sev0
  
  lin1 <- beta["beta0"] +
    beta["age"] * (age1 - 57.5)/10 +
    beta["sex"] * (sex1 - 0.5) +
    beta["sev"] * sev1 +
    params$beta_trt
  
  lambda0 <- exp(lin0)
  lambda1 <- exp(lin1)
  
  T0 <- (-log(runif(n0)) / lambda0)^(1 / shape)
  T1 <- (-log(runif(n1)) / lambda1)^(1 / shape)
  
  # Mild censoring
  C0 <- runif(n0, 0.8*tt, tt)
  C1 <- runif(n1, 0.8*tt, tt)
  
  time0 <- pmin(T0, C0, tt)
  time1 <- pmin(T1, C1, tt)
  
  event0 <- as.numeric(T0 <= C0 & T0 <= tt)
  event1 <- as.numeric(T1 <= C1 & T1 <= tt)
  
  time0 <- pmax(1, ceiling(time0))
  time1 <- pmax(1, ceiling(time1))
  
  S0 <- data.frame(time = time0, event = event0)
  S1 <- data.frame(time = time1, event = event1)
  
  ##################################################
  # 4. Utility trajectories
  ##################################################
  
  make_utility <- function(n, age, sex, sev, S, trt) {
    
    U <- matrix(NA, nrow = n, ncol = tt)
    
    for (i in 1:n) {
      
      b_i <- rnorm(1, 0, sigma_subject)
      
      for (t in 1:tt) {
        
        base_t <- params$base_fun(t)
        trt_eff_t <- ifelse(trt == 1, params$utility_fun(t), 0)
        
        u_it <- base_t +
          trt_eff_t +
          theta["age"] * (age[i] - 57.5)/10 +
          theta["sex"] * (sex[i] - 0.5) +
          theta["sev"] * sev[i] +
          b_i +
          rnorm(1, 0, sigma_noise)
        
        u_it <- min(max(u_it, 0), 1)
        
        # after death utility is zero
        if (S$event[i] == 1 & t > S$time[i]) {
          u_it <- 0
        }
        
        U[i, t] <- u_it
      }
    }
    
    return(U)
  }
  
  U0_full <- make_utility(n0, age0, sex0, sev0, S0, trt = 0)
  U1_full <- make_utility(n1, age1, sex1, sev1, S1, trt = 1)
  
  ##################################################
  # 5. Missingness
  ##################################################
  
  U0 <- U0_full
  U1 <- U1_full
  
  for (i in 1:n0) {
    for (t in 1:tt) {
      if (!(S0$event[i] == 1 & t > S0$time[i])) {
        if (rbinom(1, 1, p_miss) == 1) U0[i, t] <- NA
      }
    }
  }
  
  for (i in 1:n1) {
    for (t in 1:tt) {
      if (!(S1$event[i] == 1 & t > S1$time[i])) {
        if (rbinom(1, 1, p_miss) == 1) U1[i, t] <- NA
      }
    }
  }
  
  ##################################################
  # 6. Return
  ##################################################
  
  return(list(
    S_trt = S1,
    S_ctl = S0,
    U_trt = U1,
    U_ctl = U0,
    U_trt_full = U1_full,
    U_ctl_full = U0_full,
    age_trt = age1,
    age_ctl = age0,
    sex_trt = sex1,
    sex_ctl = sex0,
    sev_trt = sev1,
    sev_ctl = sev0,
    scenario = scenario
  ))
}
```

## 3. Missing data imputation
```{r}
fillU <- function(Ut) {
  
  Uf <- Ut
  n <- length(Uf)
  
  which_na <- which(is.na(Uf))
  which_obs <- which(!is.na(Uf))
  
  # No missing
  if (length(which_na) == 0) return(Uf)
  
  # If all values are missing, use neutral utility
  if (length(which_obs) == 0) {
    Uf[] <- 0.5
    return(Uf)
  }
  
  for (hh in which_na) {
    
    if (hh < min(which_obs)) {
      Uf[hh] <- Uf[min(which_obs)]
      
    } else if (hh > max(which_obs)) {
      Uf[hh] <- Uf[max(which_obs)]
      
    } else {
      # Missing between observed values: linear interpolation
      prev_obs <- max(which_obs[which_obs < hh])
      next_obs <- min(which_obs[which_obs > hh])
      
      Uf[hh] <- Uf[prev_obs] +
        (Uf[next_obs] - Uf[prev_obs]) *
        (hh - prev_obs) / (next_obs - prev_obs)
    }
  }
  
  return(Uf)
}

impute_matrix <- function(U) {
  t(apply(U, 1, fillU))
}
```

## 4. IPTW adjustment
```{r}
get_weights <- function(age, sex, sev, trt, trim = 10) {
  
  df <- data.frame(
    trt = trt,
    age_c = (age-57.5)/10,
    sex_c = sex-0.5,
    sev = sev
  )
  
  fit <- glm(trt ~ age_c + sex_c + sev, data = df, family = binomial)
  
  ps <- predict(fit, type = "response")
  
  p_trt <- mean(trt)
  
  w <- ifelse(
    trt == 1,
    p_trt / ps,
    (1 - p_trt) / (1 - ps)
  )
  
  w <- pmin(w, trim)
  
  return(list(
    weights = w,
    ps = ps,
    model = fit
  ))
}
```

## 5. QALY/HUS calculation
```{r}
QALY_IPTW <- function(S, U, w, tt, time_weight = NULL,
                      lam_surv = 1, lam_util = 1) {
  
  if (is.null(time_weight)) {
    time_weight <- rep(1, tt)
  }
  
  fit <- survfit(Surv(time, event) ~ 1, data = S, weights = w)
  
  S_KM <- numeric(tt)
  
  for (t in 1:tt) {
    if (length(fit$time) == 0) {
      S_KM[t] <- 1
    } else {
      idx <- which(fit$time <= t)
      S_KM[t] <- ifelse(length(idx) == 0, 1, fit$surv[max(idx)])
    }
  }
  
  U_bar <- numeric(tt)
  
  for (t in 1:tt) {
    
    alive <- which(S$time >= t)
    
    if (length(alive) == 0) {
      U_bar[t] <- 0
    } else {
      obs <- alive[!is.na(U[alive, t])]
      
      if (length(obs) == 0) {
        U_bar[t] <- 0
      } else {
        U_bar[t] <- weighted.mean(U[obs, t], w[obs])
      }
    }
  }
  
  qaly <- sum(
    time_weight *
      (S_KM ^ lam_surv) *
      (U_bar ^ lam_util)
  )
  
  return(list(
    qaly = qaly,
    survival_curve = S_KM,
    utility_curve = U_bar
  ))
}
```

# 6. Statistical tests
- 6.1 Survival-only test
- 6.2 Utility-only test
- 6.3 QALY/HUS permutation test
```{r}
# 6.1 survival only test
survival_test <- function(S1, S0, w1, w0) {
  
  S <- rbind(S1, S0)
  S$trt <- c(rep(1, nrow(S1)), rep(0, nrow(S0)))
  
  w <- c(w1, w0)
  
  fit <- coxph(
    Surv(time, event) ~ trt,
    data = S,
    weights = w,
    robust = TRUE
  )
  
  pval <- summary(fit)$coef["trt", "Pr(>|z|)"]
  
  return(pval)
}
# 6.2 utility only test
# find and compare subject level mean utility while alive 
utility_test <- function(U1, U0, S1, S0, w1, w0, nperm = 500) {
  
  U1_imp <- impute_matrix(U1)
  U0_imp <- impute_matrix(U0)
  
  subject_alive_mean <- function(U, S) {
    
    out <- numeric(nrow(U))
    
    for (i in 1:nrow(U)) {
      alive_t <- which(1:ncol(U) <= S$time[i])
      out[i] <- mean(U[i, alive_t], na.rm = TRUE)
    }
    
    return(out)
  }
  
  m1 <- subject_alive_mean(U1_imp, S1)
  m0 <- subject_alive_mean(U0_imp, S0)
  
  diff_obs <- weighted.mean(m1, w1) - weighted.mean(m0, w0)
  
  m_all <- c(m1, m0)
  w_all <- c(w1, w0)
  
  n1 <- length(m1)
  n <- length(m_all)
  
  diffs <- numeric(nperm)
  
  for (b in 1:nperm) {
    
    idx <- sample(1:n, n1)
    
    diffs[b] <-
      weighted.mean(m_all[idx], w_all[idx]) -
      weighted.mean(m_all[-idx], w_all[-idx])
  }
  
  pval <- (sum(abs(diffs) >= abs(diff_obs)) + 1) / (nperm + 1)
  
  return(pval)
}
# 6.3 QALY/HUS permutation test
qaly_test <- function(dat, nperm = 500, tt = 60,
                      lam_surv = 1, lam_util = 1,
                      time_weight = NULL) {
  
  S1 <- dat$S_trt
  S0 <- dat$S_ctl
  
  U1 <- impute_matrix(dat$U_trt)
  U0 <- impute_matrix(dat$U_ctl)
  
  age <- c(dat$age_trt, dat$age_ctl)
  sex <- c(dat$sex_trt, dat$sex_ctl)
  sev <- c(dat$sev_trt, dat$sev_ctl)
  
  trt <- c(rep(1, nrow(S1)), rep(0, nrow(S0)))
  
  # Estimate IPTW once from observed treatment assignment
  # This keeps permutation less conservative than recomputing weights each time
  w <- get_weights(age, sex, sev, trt)$weights
  
  w1 <- w[trt == 1]
  w0 <- w[trt == 0]
  
  q1 <- QALY_IPTW(S1, U1, w1, tt, time_weight, lam_surv, lam_util)$qaly
  q0 <- QALY_IPTW(S0, U0, w0, tt, time_weight, lam_surv, lam_util)$qaly
  
  diff_obs <- q1 - q0
  
  S_all <- rbind(S1, S0)
  U_all <- rbind(U1, U0)
  
  n1 <- nrow(S1)
  n <- nrow(S_all)
  
  diff_perm <- numeric(nperm)
  
  for (b in 1:nperm) {
    
    idx <- sample(1:n, n1)
    
    q1p <- QALY_IPTW(
      S_all[idx, ],
      U_all[idx, ],
      w[idx],
      tt,
      time_weight,
      lam_surv,
      lam_util
    )$qaly
    
    q0p <- QALY_IPTW(
      S_all[-idx, ],
      U_all[-idx, ],
      w[-idx],
      tt,
      time_weight,
      lam_surv,
      lam_util
    )$qaly
    
    diff_perm[b] <- q1p - q0p
  }
  
  pval <- (sum(abs(diff_perm) >= abs(diff_obs)) + 1) / (nperm + 1)
  
  return(list(
    qaly_diff = diff_obs,
    qaly_p = pval,
    qaly_trt = q1,
    qaly_ctl = q0,
    perm_distribution = diff_perm
  ))
}
```

## 7. One simulation replicate
```{r, cache=TRUE}
run_one_simulation <- function(
  scenario,
  n0 = 150,
  n1 = 150,
  tt = 60,
  nperm = 500,
  seed = NULL
) {
  
  dat <- simulate_data(
    n0 = n0,
    n1 = n1,
    tt = tt,
    scenario = scenario,
    seed = seed
  )
  
  age <- c(dat$age_trt, dat$age_ctl)
  sex <- c(dat$sex_trt, dat$sex_ctl)
  sev <- c(dat$sev_trt, dat$sev_ctl)
  trt <- c(rep(1, n1), rep(0, n0))
  
  w <- get_weights(age, sex, sev, trt)$weights

  
  w1 <- w[trt == 1]
  w0 <- w[trt == 0]
  
  surv_p <- survival_test(dat$S_trt, dat$S_ctl, w1, w0)
  
  util_p <- utility_test(
    dat$U_trt,
    dat$U_ctl,
    dat$S_trt,
    dat$S_ctl,
    w1,
    w0,
    nperm = nperm
  )
  
  qaly_obj <- qaly_test(
    dat = dat,
    nperm = nperm,
    tt = tt
  )
  
  balance <- data.frame(
    covariate = c("age", "sex", "severity"),
    trt_mean = c(mean(dat$age_trt), mean(dat$sex_trt), mean(dat$sev_trt)),
    ctl_mean = c(mean(dat$age_ctl), mean(dat$sex_ctl), mean(dat$sev_ctl)),
    trt_wmean = c(
      weighted.mean(dat$age_trt, w1),
      weighted.mean(dat$sex_trt, w1),
      weighted.mean(dat$sev_trt, w1)
    ),
    ctl_wmean = c(
      weighted.mean(dat$age_ctl, w0),
      weighted.mean(dat$sex_ctl, w0),
      weighted.mean(dat$sev_ctl, w0)
    )
  )
  
  return(list(
    scenario = scenario,
    surv_p = surv_p,
    util_p = util_p,
    qaly_p = qaly_obj$qaly_p,
    qaly_diff = qaly_obj$qaly_diff,
    balance = balance,
    data = dat
  ))
}

run_all_scenarios_once <- function(
  scenarios = c("A", "B", "C", "D", "E", "F", "G"),
  n0 = 100,
  n1 = 100,
  tt = 60,
  nperm = 500,
  seed = 123
) {
  
  results <- data.frame(
    scenario = scenarios,
    surv_p = NA_real_,
    util_p = NA_real_,
    qaly_p = NA_real_,
    qaly_diff_months = NA_real_,
    qaly_diff_years = NA_real_,
    mean_sev_trt_raw = NA_real_,
    mean_sev_ctl_raw = NA_real_,
    mean_sev_trt_wt = NA_real_,
    mean_sev_ctl_wt = NA_real_,
    stringsAsFactors = FALSE
  )
  
  for (k in seq_along(scenarios)) {
    
    s <- scenarios[k]
    
    cat("Running scenario:", s, "\n")
    
    one <- run_one_simulation(
      scenario = s,
      n0 = n0,
      n1 = n1,
      tt = tt,
      nperm = nperm,
      seed = seed
    )
    
    results$surv_p[k] <- one$surv_p
    results$util_p[k] <- one$util_p
    results$qaly_p[k] <- one$qaly_p
    results$qaly_diff_months[k] <- one$qaly_diff
    results$qaly_diff_years[k] <- one$qaly_diff / 12
    
    balance <- one$balance
    
    sev_row <- balance[balance$covariate == "severity", ]
    
    results$mean_sev_trt_raw[k] <- sev_row$trt_mean
    results$mean_sev_ctl_raw[k] <- sev_row$ctl_mean
    results$mean_sev_trt_wt[k] <- sev_row$trt_wmean
    results$mean_sev_ctl_wt[k] <- sev_row$ctl_wmean
  }
  
  results$surv_sig <- results$surv_p < 0.05
  results$util_sig <- results$util_p < 0.05
  results$qaly_sig <- results$qaly_p < 0.05
  
  results <- merge(
    results,
    expected_reference,
    by = "scenario",
    all.x = TRUE
  )
  
  return(results)
}
```

The expected p-value tables as follows
```{r, include=FALSE}
expected_reference <- data.frame(
  scenario = c("A", "B", "C", "D", "E", "F", "G"),
  
  scenario_name = c(
    "Null",
    "Survival benefit only",
    "Utility benefit only",
    "Early harm, late benefit",
    "Longer survival, worse QoL",
    "Better QoL, shorter survival",
    "Modest survival + modest utility benefit"
  ),
  
  true_survival_effect = c(
    "None",
    "Benefit",
    "None",
    "Small/moderate benefit",
    "Benefit",
    "Harm",
    "Small benefit"
  ),
  
  true_utility_effect = c(
    "None",
    "None",
    "Benefit",
    "Early harm then late benefit",
    "Harm",
    "Benefit",
    "Small benefit"
  ),
  
  expected_survival_test = c(
    "Not significant",
    "Likely significant",
    "Not significant",
    "May be weak",
    "May be significant",
    "May be significant in harmful direction",
    "May be weak"
  ),
  
  expected_utility_test = c(
    "Not significant",
    "Not significant",
    "Likely significant",
    "May be weak because effects vary over time",
    "May detect worse utility",
    "May detect better utility",
    "May be weak"
  ),
  
  expected_qaly_test = c(
    "Not significant",
    "Likely significant due to survival component",
    "Likely significant due to utility component",
    "Often stronger than individual tests, especially with time weighting",
    "May be attenuated because survival and utility oppose each other",
    "May be attenuated because survival and utility oppose each other",
    "Expected to be strongest because both domains improve modestly"
  ),
  
  desired_message = c(
    "Type I error control",
    "QALY captures survival benefit while utility-only fails",
    "QALY captures utility benefit while survival-only fails",
    "QALY captures time-varying joint benefit",
    "Trade-off: composite endpoint reflects net benefit, not one marginal outcome",
    "Trade-off: composite endpoint reflects net benefit, not one marginal outcome",
    "Best example that QALY/HUS is more comprehensive"
  ),
  
  stringsAsFactors = FALSE
)
```

Running scenarios for one round of simulaion
```{r, cache=TRUE}
one_run_results <- run_all_scenarios_once(
  scenarios = c("A", "B", "C", "D", "E", "F", "G"),
  n0 = 150,
  n1 = 150,
  tt = 60,
  nperm = 500
)

one_run_results
```



## 8. Repeated simulation study / power table
```{r}
run_power_study <- function(
  scenarios = c("A", "B", "C", "D", "E", "F", "G"),
  nsim = 30,
  nperm = 100,
  n0 = 150,
  n1 = 150,
  tt = 60,
  alpha_level = 0.05,
  seed = 100
) {
  
  all_results <- data.frame()
  
  for (s in scenarios) {
    
    cat("Running scenario:", s, "\n")
    
    scenario_results <- data.frame(
      scenario = s,
      sim = 1:nsim,
      surv_p = NA,
      util_p = NA,
      qaly_p = NA,
      qaly_diff = NA
    )
    
    for (r in 1:nsim) {
      
      one <- run_one_simulation(
        scenario = s,
        n0 = n0,
        n1 = n1,
        tt = tt,
        nperm = nperm,
        seed = seed + 1000 * match(s, scenarios) + r
      )
      
      scenario_results$surv_p[r] <- one$surv_p
      scenario_results$util_p[r] <- one$util_p
      scenario_results$qaly_p[r] <- one$qaly_p
      scenario_results$qaly_diff[r] <- one$qaly_diff
    }
    
    all_results <- rbind(all_results, scenario_results)
  }
  
  summary_results <- aggregate(
    cbind(
      surv_sig = surv_p < alpha_level,
      util_sig = util_p < alpha_level,
      qaly_sig = qaly_p < alpha_level,
      qaly_diff = qaly_diff
    ) ~ scenario,
    data = all_results,
    FUN = mean
  )
  
  names(summary_results) <- c(
    "scenario",
    "survival_power",
    "utility_power",
    "qaly_power",
    "mean_qaly_diff"
  )
  
  return(list(
    raw = all_results,
    summary = summary_results
  ))
}
study <- run_power_study(nsim = 30, nperm = 100, seed= 100)
study$summary
```

# Significance heatmap
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

power_heatmap_data <- study$summary %>%
  select(
    scenario,
    survival_power,
    utility_power,
    qaly_power
  ) %>%
  pivot_longer(
    cols = c(survival_power, utility_power, qaly_power),
    names_to = "test",
    values_to = "rejection_rate"
  ) %>%
  mutate(
    test = recode(
      test,
      survival_power = "Survival-only",
      utility_power = "Utility-only",
      qaly_power = "QALY/HUS"
    ),
    scenario = factor(scenario, levels = c("A", "B", "C", "D", "E", "F", "G")),
    test = factor(test, levels = c("Survival-only", "Utility-only", "QALY/HUS")),
    label = sprintf("%.2f", rejection_rate)
  ) %>%
  mutate(
    scenario_label = recode(
      as.character(scenario),
      A = "A: Null",
      B = "B: Survival only",
      C = "C: Utility only",
      D = "D: Early harm/late benefit",
      E = "E: Longer survival/worse QoL",
      F = "F: Better QoL/shorter survival",
      G = "G: Both benefit"
    ),
    scenario_label = factor(
      scenario_label,
      levels = c(
        "A: Null",
        "B: Survival only",
        "C: Utility only",
        "D: Early harm/late benefit",
        "E: Longer survival/worse QoL",
        "F: Better QoL/shorter survival",
        "G: Both benefit"
      )
    )
  )

fig_power_heatmap_labeled <- ggplot(
  power_heatmap_data,
  aes(x = scenario_label, y = test, fill = rejection_rate)
) +
  geom_tile(color = "white", linewidth = 1) +
  geom_text(aes(label = label), size = 3.8) +
  scale_fill_gradient(
    low = "#F7F7F7",
    high = "#2C7BB6",
    limits = c(0, 1),
    name = "Rejection rate"
  ) +
  labs(
    title = "Empirical Rejection Rates Across Simulation Scenarios",
    subtitle = "Scenario A = type I error; Scenarios B-G = empirical power",
    x = "Simulation Scenario",
    y = "Test"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 35, hjust = 1),
    panel.grid = element_blank()
  )

fig_power_heatmap_labeled



heatmap_data <- one_run_results %>%
  select(scenario, surv_p, util_p, qaly_p) %>%
  pivot_longer(
    cols = c(surv_p, util_p, qaly_p),
    names_to = "test",
    values_to = "p_value"
  ) %>%
  mutate(
    test = recode(
      test,
      surv_p = "Survival-only",
      util_p = "Utility-only",
      qaly_p = "QALY/HUS"
    ),
    scenario = factor(scenario, levels = c("A", "B", "C", "D", "E", "F", "G")),
    test = factor(test, levels = c("Survival-only", "Utility-only", "QALY/HUS")),
    result = ifelse(p_value < 0.05, "Significant", "Not significant"),
    p_label = ifelse(p_value < 0.001, "<0.001", sprintf("%.3f", p_value))
  )

fig_heatmap <- ggplot(
  heatmap_data,
  aes(x = scenario, y = test, fill = result)
) +
  geom_tile(color = "white", linewidth = 1) +
  geom_text(aes(label = p_label), size = 4) +
  scale_fill_manual(
    values = c(
      "Significant" = "#2C7BB6",
      "Not significant" = "#D9D9D9"
    )
  ) +
  labs(
    title = "Significance Pattern Across Simulation Scenarios",
    x = "Simulation Scenario",
    y = "Test",
    fill = "Result"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    panel.grid = element_blank()
  )

fig_heatmap
```

